---
title: "COVID 19 dashboard"
author: "Shahadat Hossain"
date: "20 April 2020"
output:
  slidy_presentation: default
  html_document:
    number_sections: yes
    toc: yes
  ioslides_presentation: default
mode: selfcontained
job: Reproducible Pitch Presentation
subtitle: For the United States
---

## Overview
This is an RStudio shiny application developed as a part of final project in the Developing Data Products course in Coursera Data Science Specialization track. The application is a dashboard to monitor COVID-19 situation in the United States.

### Essential links

- GitHub Repo for R files: *https://github.com/shossainghub/Developing-Data-Products*
- Rpub link for Presentation: *https://rpubs.com/shahadat_099/602466*
- The application is hosted at: *https://shossain.shinyapps.io/COVID-19_USA*
- Project instruction: *https://www.coursera.org/learn/data-products/peer/tMYrn/course-project-shiny-application-and-reproducible-pitch*

---

## The leaflet map (code)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(leaflet)
library(leaflet.extras)
library(tidyverse)
library(readr)
library(plotly)

us.covid.df <- read_rds(path = "us.covid.df.rds")
```


```{r}
map <- us.covid.df %>%
    filter(date == max(date)) %>%
    mutate(label = paste0(type, ": ", as.character(cum)),
           Combined_Key = paste(Province_State, "US", sep = ", ")) %>%
    group_by(Combined_Key) %>%
    mutate(label = paste(label, collapse = "<br>")) %>%
    ungroup() %>%
    filter(type %in% "Confirmed cases") %>% 
    leaflet() %>%
    addTiles() %>%
    setView(lng = -97, lat = 38, zoom = 4) %>%
    addCircleMarkers(~Long, ~Lat,
                     popup = ~paste("State: <b>", Combined_Key, "</b> <br>",
                                    "Date: ", date, "<br>",
                                    label),
                     label = ~Combined_Key,
                     color = ~color,
                     radius = ~log(cum)*1.3,
                     stroke = F,
                     fillOpacity = 0.6, weight = 15) %>% 
    addEasyButton(easyButton(
        icon    = "glyphicon glyphicon-globe", title = "Reset zoom",
        onClick = JS("function(btn, map){ map.setView([38, -97], 4); }")))
```


## The leaflet map (graph)

```{r, fig.cap="Total Confirmed cases in the US", fig.align='center', fig.width=18, fig.height=8}
map
```

---

## Total number of Confirmed cases

```{r, fig.align='center'}
us.covid.df %>%  group_by(type, date, color) %>%  summarise(cum = sum(cum)) %>% 
    ungroup() %>% group_by(type) %>%  plot_ly(x = ~date, y=~cum, name = ~type,
              type = 'scatter', mode = 'lines+markers', 
              opacity=0.7,  line = list(color = ~color, width = 3),
              marker = list(color = ~color, width = 3)) %>% 
      layout(xaxis = list(title = ""), yaxis = list(title = ""), legend = list(orientation = 'h'))
```

